Energy and the CES production function

### 2015-11-13 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now can evaluate Other_Models.
rbind.fill -> bind_rows

FittedAndResid <- plyr::rbind.fill(temp_data_exp, temp_data_CSP, temp_data_noCSP)

<<TableData>>=
  TableData <- 
  AllCoeffs %>%
  plyr::rename(c(model = "Model", energy = "Energy", nest = "Nest")) %>%
  mutate(Nest = 
           plyr::mapvalues(
             Nest,
             from=c("kl", "kle", "lek", "ekl"),
             to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
         CSP =  
           plyr::mapvalues(
             CSP, 
             from=c("w/ CSP", "w/o CSP"), 
             to=c("Adhere", "Reject")),
         Energy =
           plyr::mapvalues(
             Energy, 
             from=c("Without energy", "With energy"), 
             to=c("Without", "With")),
         Model = 
           plyr::mapvalues(
             Model, 
             from=c("exp"), 
             to=c("Ref."))
  )
@

@@

<<Other_Models, eval=FALSE>>=
# These models were estimated and the results sent to Paul Brockway.
# At this point, there is no reason to estimate the modesl every time.

# PT, unadjusted kl, quality-adjusted e
mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
# PT, quality-adjusted kl, unadjusted e
mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))

# UK, unadjusted kl, quality-adjusted e
mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
# UK, quality-adjusted kl, unadjusted e
mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
@

>>>>

FittedAndResid <- bind_rows(temp_data_exp, temp_data_CSP, temp_data_noCSP)
@

<<TableData>>=
  TableData <- 
  AllCoeffs %>%
#  rename_(Model = "model", Energy = "energy", Nest = "nest") %>%
  mutate(Nest = 
           plyr::mapvalues(
             nest,
             from=c("kl", "kle", "lek", "ekl"),
             to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
         CSP =  
           plyr::mapvalues(
             CSP, 
             from=c("w/ CSP", "w/o CSP"), 
             to=c("Adhere", "Reject")),
         Energy =
           plyr::mapvalues(
             energy, 
             from=c("Without energy", "With energy"), 
             to=c("Without", "With")),
         Model = 
           plyr::mapvalues(
             model, 
             from=c("exp"), 
             to=c("Ref."))
  )
@

@@
